### 2019-09-09 papers/journal/intro.tex
Added rebuttal outline
Updates from Overleaf

\noindent 
%A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
Eukaryotic cells contain distinct membrane-bound objects known as organelles: endoplasmic reticulum (ER), Golgi apparatus, vacuoles, and lysosomes are examples of these.
%These compartments exchange molecules amo\-ngst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
%
%%The molecular interaction network that controls the vesicle traffic system involves dozens of varieties of molecules that regulate the flow of cargo. 
%
%%Due to this, obtaining a complete understanding of the VTS through physical experimentation alone is a hard problem.
%
%%Highly reduced models of vesicle traffic have previously provided insight into how the chemical composition of various cellular compartments can emerge out of molecular regulation and cargo flow. 
%
%%However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016stacking}. 
%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
%%In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the effectiveness of such methods.
%
%
Some of the material of the cell needs to move
between these organelles in small membrane-bound
transporters known as vesicles \cite{stenmark2009rab}.
%
This organization resembles a transport logistics network
and is commonly known as the membrane traffic system.
%
Membrane traffic underpins nearly every aspect of eukaryotic cellular
physiology, including human cellular physiology.
%
Defects in membrane traffic lead to a variety of disorders or even
cell death \cite{stenmark2009rab}.
%
Understanding how membrane traffic functions are, therefore, one of the
central challenges of cell biology.
%

The cell biologists have made some progress by assembling a
“parts list” of molecules that drive vesicle
traffic~\cite{dacks2007evolution}.
%
The essential processes involve the creation of vesicles loaded with
cargo from source organelles, known as “budding”, and the depositing
of those vesicles and cargo into target organelles, known as “fusion”
\cite{munro2004organelle}.
%
Proteins that are called coats and the adaptors that select the cargo regulate budding.
%
The proteins that are known as SNAREs and tethers that ensure that vesicles
fuse to the correct target regulate fusion
\cite{mani2016stacking}.
%
Although we know a great deal about molecular-level details, there has
been very little work done on how such processes are integrated across
scales to build the entire vesicle traffic system (VTS).
%
We have recently attempted to use the ideas of graph theory to address
this question \cite{mani2016stacking,shukla2017discovering}.

@@

Nonetheless, completing the VTS for different organisms is very useful. 
%
The malfunction of the VTS causes many diseases.
%
The knowledge of the complete network would help identify the root causes of
the diseases~\cite{bexiga2013human,gissen2007cargos}. 
%
At a more basic level, having complete pictures of the VTS for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network. 
%
The network knowledge would also allow us to decipher features such as parts of the traffic system that is unchanging and therefore likely to be its core, and more plastic parts~\cite{barlow2017seeing}.

@@

In contrast, here we seek to understand the properties of vesicle traffic networks
over all possible update rules, not just for a sampled subset.
%
Formal verification tools like model checkers, SAT (Boolean satisfiability), SMT (satisfiability modulo theories) and QBF (quantified Boolean formula) solvers serve precisely this purpose. 
%
%Formal verification tools, such as model checkers
%\cite{clarke1996symbolic, biere2003bounded, clarke2008birth,
%	cimatti2000nusmv, holzmann1997model} and SAT solvers
%\cite{moskewicz2001chaff,een2004extensible} serve precisely this
%purpose.
%%
The tools model the computation symbolically for the graphs of finite size and can predict the hypothesis for all possible states of the system without explicit enumeration of rules. 
%
In recent work~\cite{shukla2017discovering}, we employed the model checker CBMC \cite{ckl2004} meant to analyze ANSI C programs for studying this problem. 
%
VTSs and SNARE regulations were modeled as C code using arrays to represent graphs and Boolean tables. 
%
The graph connectivity question for different variations of SNARE regulations was modeled as logical assertions to be checked by the model checker. 
%
Although the performance was satisfactory, the encoding was non-optimal and hence scalability of the method was insufficient. The tool was able to handle the system with just eight compartments.
%
Another interesting question of property involving quantifiers (was termed as sufficient condition in \cite{shukla2017discovering}; in this paper, we call it universal condition) was partly handled
using sampling and left open.
%
In~\cite{smtVTS}, we developed more efficient direct encoding to SMT solvers. 
%
We also worked on the synthesis of the unknown pieces may
be {\em assisted} by computation on the graph model of VTSs~\cite{synthesisGupta}.
%
In the work, we developed encoding for the synthesis problem.
%
This paper brings together the above encodings with extended experiments and more detailed
expositions for the benefit of both biological and computation community.
We additionally explored QBF based encoding of some of the problems.

>>>>

\noindent 
%A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
Eukaryotic cells contain distinct membrane-bound objects known as organelles: endoplasmic reticulum (ER), Golgi apparatus, vacuoles, and lysosomes are examples of these.
%These compartments exchange molecules amo\-ngst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
%
%%The molecular interaction network that controls the vesicle traffic system involves dozens of varieties of molecules that regulate the flow of cargo. 
%
%%Due to this, obtaining a complete understanding of the VTS through physical experimentation alone is a hard problem.
%
%%Highly reduced models of vesicle traffic have previously provided insight into how the chemical composition of various cellular compartments can emerge out of molecular regulation and cargo flow. 
%
%%However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016stacking}. 
%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
%%In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the effectiveness of such methods.
%
%
Some of the material of the cell needs to move
between these organelles in small membrane-bound
transporters known as vesicles \cite{stenmark2009rab}.
%
This organization resembles a transport logistics network
and is commonly known as the membrane traffic system.
%
Membrane traffic underpins nearly every aspect of eukaryotic cellular
physiology, including human cellular physiology.
%
Defects in membrane traffic lead to a variety of disorders or even
cell death \cite{stenmark2009rab}.
%
Understanding how membrane traffic functions is, therefore, one of the
central challenges of cell biology.
%

Cell biologists have made some progress by assembling a
“parts list” of molecules that drive vesicle
traffic~\cite{dacks2007evolution}.
%
The essential processes involve the creation of vesicles loaded with
cargo from source organelles, known as “budding”, and the depositing
of those vesicles and cargo into target organelles, known as “fusion”
\cite{munro2004organelle}.
%
Proteins that are called coats and the adaptors that select the cargo regulate budding.
%
The proteins that are known as SNAREs and tethers that ensure that vesicles
fuse to the correct target regulate fusion
\cite{mani2016stacking}.
%
Although we know a great deal about molecular-level details, there has
been very little work done on how such processes are integrated across
scales to build the entire vesicle traffic system (VTS).
%
We have recently attempted to use the ideas of graph theory to address
this question \cite{mani2016stacking,shukla2017discovering}.

@@

Nonetheless, completing the VTS for different organisms is very useful. 
%
The malfunction of the VTS causes many diseases.
%
The knowledge of the complete network would help identify the root causes of
the diseases~\cite{bexiga2013human,gissen2007cargos}. 
%
At a more basic level, having complete pictures of the VTS for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network. 
%
The network knowledge would also allow us to decipher features such as parts of the traffic system that are unchanging and therefore likely to be its core, and more plastic parts~\cite{barlow2017seeing}.

@@

In contrast, here we seek to understand the properties of vesicle traffic networks
over all possible update rules, not just for a sampled subset.
%
Formal verification tools like model checkers, SAT (Boolean satisfiability), SMT (satisfiability modulo theories) and QBF (quantified Boolean formula) solvers serve precisely this purpose. 
%
%Formal verification tools, such as model checkers
%\cite{clarke1996symbolic, biere2003bounded, clarke2008birth,
%	cimatti2000nusmv, holzmann1997model} and SAT solvers
%\cite{moskewicz2001chaff,een2004extensible} serve precisely this
%purpose.
%%
The tools model the computation symbolically for the graphs of finite size and can predict the hypothesis for all possible states of the system without explicit enumeration of rules. 
%
In recent work~\cite{shukla2017discovering}, we employed the model checker CBMC \cite{ckl2004} meant to analyze ANSI C programs for studying this problem. 
%
VTSs and SNARE regulations were modeled as C code using arrays to represent graphs and Boolean tables. 
%
The graph connectivity question for different variations of SNARE regulations was modeled as logical assertions to be checked by the model checker. 
%
Although the performance was satisfactory, the encoding was non-optimal and hence scalability of the method was insufficient. The tool was able to handle the system with just eight compartments.
%
Another interesting question of property involving quantifiers (was termed as sufficient condition in \cite{shukla2017discovering}; in this paper, we call it universal condition) was partly handled
using sampling and left open.
%
In~\cite{smtVTS}, we developed more efficient direct encoding to SMT solvers. 
%
We also worked on the synthesis of the unknown pieces that may
be {\em assisted} by computation on the graph model of VTSs~\cite{synthesisGupta}.
%
In the work, we developed an encoding for the synthesis problem.
%
This paper brings together the above encodings with extended experiments and more detailed
expositions for the benefit of both biological and computation community.
We additionally explored QBF based encoding of some of the problems.
